\documentclass[margin,line]{res}

\oddsidemargin -.7in
\evensidemargin -.7in
\textwidth=6.3in
\itemsep=0in
\parsep=0in
\setlength{\parskip}{0.2cm plus1mm minus1mm}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Vivek Nair \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
3224 EBII, 890 Oval Drive            & {\it Phone:}  (919) 523-9920 \\            
%1241 University CT            & {\it Phone:}  (919) 792-8641 \\
Raleigh   & {\it E-mail:}  vnair2@ncsu.edu\\         
NC, 27606 &  
  {\it www:} https://sites.google.com/site/vivekaxl/ \\
\end{tabular}

%\section{\sc Objective}
%Seeking a Summer Internship position starting from May,2014.


\section{\sc Education}
{\bf North Carolina State University } \hfill Raleigh, NC\\
\quad Ph.D. candidate in Computer Science  \hfill  Summer 2013 -  Current\\
Advisor: Dr. Tim Menzies\\
\quad Current GPA: 3.85/4.0 

{\bf National Institute of Technology, Durgapur } \hfill Durgapur,India \\
\quad M.Tech in Information Technology \hfill {\it 2011} \\
\quad GPA: 8.93/10


{\bf West Bengal University of Technology } \hfill Kolkata, India \\
\quad B.Tech in Computer Science \hfill {\it 2009} \\
\quad GPA: 7.23/10

\section{\sc Professional Experience}

{\bf Research Assistant} \hfill North Carolina State University (NCSU) \\
\textit{Real-world Artifical Intelligence for Software Engineering (RAISE)} 
\hspace{1cm} \hfill {\it January,2015 onwards}
\begin{itemize}
	\item \textbf{Recommendation System for Data Analyst}\\
	Analytics process is undertaken by users to mine large data sets, and this process is adhoc and highly customized. Recommendation system, which learns from code written by expert
	programmers, can be used to bridge the gap between the expert data analysts and novice data analysts. Code is analyzed to build a Markov-model, which is then be used 
	to provide recommendations to users. In our initial experiments, use of tf-idf (term frequency inverse document frequency) has been proven useful for dimensionality 
	reduction.\\
	Languages used: Python\\
\end{itemize}

{\bf Teaching Assistant} \hfill North Carolina State University (NCSU) \\
\textit{Design and Analysis of Algorithm(CSC505)} \hspace{1cm} \hfill {\it January,2014 - December,2014}
	\begin{itemize}
		\setlength{\itemsep}{-10pt}
		\item Hold weekly office hours and grade exams.
	\end{itemize}

{\bf Research Assistant} \hfill North Carolina State University (NCSU) \\
\textit{Distributed Systems Research Group on Autonomy, ResilieNce, Collaboration, and Energy (DANCE)} 

\hspace{10cm} \hfill {\it May,2013 - December,2013}
\begin{itemize}
	\item \textbf{Detecting Contention in Data Center Environment}\\
	Interference in a data center leads to performance variability, which causes losses to data center operators. Dynamically detecting and mitigating interference
	would save money for the operators. Use of hardware performance counters have proved useful in our initial experiments.\\
	Languages used: Python, Shell script \\
	Various systems used as the testbed: Hadoop, Web service (RUBiS and httpperf)\\
\end{itemize}	
\textbf{Software Engineer} \hfill Samsung Software Engineering Labs, India \\ 
\textit{File System \& Memory Team}\hfill {\it June 2011 - May 2013}
	\begin{itemize}
		\setlength{\itemsep}{-10pt}
		\item Worked on various projects based on NOR Flash for Ultra Low Cost cell phones.\\
		\item Developed tools to write data into One Time Programmable area of the NOR Flash.\\
		\item Worked on various filesystems like TargetFFS-NAND, Target-NOR, TargetZFS and Target FAT.
		Languages used: C\\
	\end{itemize}

\newpage
\textbf{Research Assistant} \hfill National Institute of Technology, Durgapur \\ 
\textit{Under Guidance of S. Choudhury}\hfill {\it March 2010 - May 2011}
	\begin{itemize}
		\item \textbf{An Integrated Routing, Scheduling and Assembly scheme for OBS network}\\
		The proposed schemes for OBS networks minimize the burst loss probability of individual bursts and at the same time achieve the goal of maximization of the 
		minimum unutilized bandwidth of links in Optical Burst Switched networks.\\
		Languages used: Java, Shell script\\
	\end{itemize}		
	
%\textbf{Software development intern} \hfill Vinapo Corp., Vietnam \\
%\textit{Software development team} \hfill {\it May 2006 - November 2006}	%
%	\begin{itemize}
%		\item Participate in developing an e-commerce application allowing clients to generate an online store by themself. My main task was to implement the web framework to let user customize their own websites. \\
%		Languages used: C\#, Javascript, HTML, SQL.
%	\end{itemize}
\section{\sc Technical Skills} 
\begin{itemize}
\item Language: C (6+ years), Java (2+ years), Python (15 months), Shell script
\item OS: Linux, Windows
\item Version Control: Perforce, git
\end{itemize}

\section{\sc Publications}
\begin{itemize}
\item Subhrabrata Choudhury, \textbf{Vivek Nair}, Jaydeep Howlader, Bikash Choudhury and A.K. Mal. \textit{``An integrated routing and offset-time adaptation scheme for OBS network''} in ICDCN,2015 (to appear).
%\item Daniel Dean, Hiep Nguyen, Xiaohui Gu, Hui Zhang, Junghwan Rhee,  Nipun Arora. \textit{``Finding a Needle in Haystack: Online Performance Anomaly Root Cause Inference for Virtualized Hosting Infrastructures"}. Under submission.
\item Subhrabrata Choudhury, \textbf{Vivek Nair}, A.K. Mall. \textit{`A Routing Scheme for OBS Networks"}, in Journal of Optical Communications and Networking(JOCN), 2013.
%\item Hiep Nguyen, Daniel Dean, Kamal KC, Xiaohui Gu. \textit{``Insight: Enable In-situ Shadow Debugging for Production Systems using Onsite Failure Execution Reproduction"}. Under submission.
\item Subhrabrata Choudhury, \textbf{Vivek Nair}, Bikash Choudhury, Pallab Biswas, A.K. Mall. \textit{`A family of flexible offset-time based wavelength schedulers for OBS edge-nodes"}, in ICP,2012.
\item Pallab Biswas, \textbf{Vivek Nair},Soumen Nandi,Soumendra Nath Biswas,Amitav Biswas,Animesh Dutta. \textit{`Session management protocol for virtual classroom in teleteaching"}, in ICCIT, 2010.
\item Animesh Dutta, \textbf{Vivek Nair}, Ranjan Dasgupta, Swapan Bhattacharya. \textit{``Ontology Based Semiformal Design of Teleteaching System"}, in TENCON, 2010.
\item \textbf{Vivek Nair}, Animesh Dutta. \textit{``Ontology based Session Management Protocol for Teleteaching Domain"}. ICCAE, 2010.
%\item D. Nguyen, H. Nguyen, T. Nguyen and W. Shi. \textit{`` Trouble Dashboard: A Distributed Failure Monitoring System for High-End Computing"}. Proc. of the 2009 IEEE-RIVF International Conference on Computing and Telecommunication Technologies, 2009.
\end{itemize}

\section{\sc Honors and Awards} 
\begin{itemize}
    \item Awarded the Employee of the Month in the month of January,2012 at Samsung Engineering Lab
    \item Awarded Scholarship by the HRD Ministry for pursuing M.Tech
\end{itemize}

%\section{\sc References}
%Dr. Tim Menzies\\
%Professor\\
%Department of Computer Science\\ 
%tim.menzies@gmail.com\\


\end{resume}
\end{document}



